Generating Interactive WebSocket Applications in TypeScript

### 2020-03-09 PLACES_2020/encoding.tex
PLACES: address FZ comments

\subsubsection{Linear Channel Usage}
\label{section:serverlinear}
\fz{This sentence is confusing and I don't know how to fix.}
Channel linearity is guaranteed based on the correctness of our library design
and session runtime implementation, which means a faulty implementation could
violate this, but is up to the library author to verify once rather than the
end user. Our library design prevents the two conditions detailed below:

@@

\paragraph{Unused Channels}
The initial state must be supplied to the session runtime
constructor in order to instantiate a session;
this initial state is defined
in terms of the successor states, which in turn has references to its
successors and so forth.
\fz{It's not the approach, rather than the developer implementation?}
This encoding approach covers the terminal state (if it exists), and the
session runtime guarantees this terminal state, if it exists, will be reached
by construction.

>>>>

\subsubsection{Linear Channel Usage}
\label{section:serverlinear}
\fz{This sentence is confusing and I don't know how to fix.}

Developers writing their implementation using the generated APIs 
enjoy channel linearity by construction.
Our library design prevents the two conditions detailed below:

@@

\paragraph{Unused Channels}
The initial state must be supplied to the session runtime
constructor in order to instantiate a session;
this initial state is defined
in terms of the successor states, which in turn has references to its
successors and so forth.
\fz{It's not the approach, rather than the developer implementation?}

The developer's implementation will cover the terminal state
(if it exists), and the
session runtime guarantees this terminal state will be reached
by construction.
